### 2024-06-05 player-evaluation.qmd
20240604 - links

[ADD LINKS TO SOURCES OF RANKINGS/PROJECTIONS/ADP/AAV, ETC]

>>>>

Fantasy rankings are provided by many sources.
[FantasyPros](https://www.fantasypros.com/nfl/rankings/consensus-cheatsheets.php) aggregates fantasy rankings across sources.
[Fantasy Football Analytics](https://fantasyfootballanalytics.net) creates fantasy rankings from projections that are aggregated across sources (see the webapp here: <https://apps.fantasyfootballanalytics.net>).

Average Draft Position (ADP) data are provided by [FantasyPros](https://www.fantasypros.com/nfl/adp/overall.php).
Average Auction Value (AAV) data are also provided by [FantasyPros](https://www.fantasypros.com/nfl/auction-values/calculator.php).

Projections that are aggregated across sources are provided by [Fantasy Football Analytics](https://fantasyfootballanalytics.net) (see the webapp here: <https://apps.fantasyfootballanalytics.net>) and by [FantasyPros](https://www.fantasypros.com/nfl/auction-values/calculator.php).
